---
output: 
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r echo=FALSE}
# We jump through these hoops to make sure we're re-using the same cache path
cache.path = if (file.exists(file.path(getwd(),"docs"))) {
               file.path(getwd(),"docs","README_cache/")
             } else {
               file.path(getwd(),"README_cache/")
             }
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  cache.path = cache.path
)

library(edgarWebR)
```
# edgarWebR

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/edgarWebR)](https://cran.r-project.org/package=edgarWebR)
[![Travis-CI Build Status](https://travis-ci.org/mwaldstein/edgarWebR.svg?branch=master)](https://travis-ci.org/mwaldstein/edgarWebR)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mwaldstein/edgarWebR?branch=master&svg=true)](https://ci.appveyor.com/project/mwaldstein/edgarWebR)
[![codecov.io](https://codecov.io/github/mwaldstein/edgarWebR/coverage.svg?branch=master)](https://codecov.io/github/mwaldstein/edgarWebR?branch=master)


* Author/Maintainer: [Micah J Waldstein](https://micah.waldste.in)
* License: [MIT](https://opensource.org/licenses/MIT)

## Introduction
edgarWebR provides an interface to access the [SEC's EDGAR
system](https://www.sec.gov/edgar/searchedgar/webusers.htm) for company
financial filings.

EdgarWebR does *not* provide any functionality to extract financial data or
other information from filings, only the metadata and company information. For
processing of the financia data.

## EDGAR Tools

The EDGAR System provides a number of [tools](https://www.sec.gov/edgar/searchedgar/webusers.htm)
for filing and entity lookup and examination. edgarWebR will eventually support
all of the provided tools, but for now it is focused on covering company and
fund search and resultant filings.

*Search Interfaces:*

| Tool                          | URL                                                             | edgarWebR function(s) |
|-------------------------------|-----------------------------------------------------------------|-----------------------|
| Company                       | https://www.sec.gov/edgar/searchedgar/companysearch.html        | `company_search()`, `company_information()`, `company_details()`, `company_filings()` |
| Recent Filings                | https://www.sec.gov/cgi-bin/browse-edgar?action=getcurrent      | `latest_filings()` |
| Full Text                     | http://searchwww.sec.gov/EDGARFSClient/jsp/EDGAR_MainAccess.jsp | `full_text()` |
| Header Search                 | https://www.sec.gov/cgi-bin/srch-edgar                          | `header_search()` |
| Fund Disclosures              | https://www.sec.gov/edgar/searchedgar/prospectus.htm            | Use `company_search()` and specify the 'type' parameter as 485 |
| Fund Voting Records           | https://www.sec.gov/edgar/searchedgar/n-px.htm                  | Use `company_search()` and specify the 'type' parameter as 'N-PX' |
| Fund Search                   | https://www.sec.gov/edgar/searchedgar/mutualsearch.html         | `fund_search()`, `fund_fast_search()` |
| Var. Insurance Products       | https://www.sec.gov/edgar/searchedgar/vinsurancesearch.html     | `variable_insurance_search()`, `variable_insurance_fast_searc()` |
| Confidential treatment orders | https://www.sec.gov/edgar/searchedgar/ctorders.htm              | Use `header_search()`, `company_search()`, `latest_filings()`, or `full_text()` and use form types 'CT ORDER'|
| Effectiveness notices         | https://www.sec.gov/cgi-bin/browse-edgar?action=geteffect       | N/A |
| CIK                           | https://www.sec.gov/edgar/searchedgar/cik.htm                   | `cik_search()` |
| Daily Filings                 | https://www.sec.gov/edgar/searchedgar/currentevents.htm         | `current_events()` |
| Correspondence                | https://www.sec.gov/answers/edgarletters.htm                    | Use `header_search()`, `company_search()`, `latest_filings()`, or `full_text()` and use form types 'upload' or 'corresp'|

Once a filing is found via any of the above, there are a number of functions to
process the result -

 * `filing_documents()`
 * `filing_filers()`
 * `filing_funds()`
 * `filing_information()`
 * `filing_details()` - returns all 4 of the filing components in a list.

### Parsing Tools

While edgarWebR is primarily focused on providing an interface to the online
SEC tools, there are a few activities for handling filing documents for which
no current tools exist.

 * `parse_submission()` - takes a full submission SGML document and parses out
   compontent documents. Most of the time, the documents of interest in a
   particular submission will be online and accessible via
   `filing_documents()` - this function is to unpack the raw submission to get
   all the doucments. You may also find it more efficient if you're regularly
   downloading all of the files in a given submission.
 * `parse_filing()` - Takes a HTML narrative filing and annotates each
   paragraph with item and part numbers.

### Data Sets

There is one dataset provieded with edgarWebR - **sic_codes**, providing a
catalog of SIC codes and their hierarchy.

### URL Tools

There are also a number of utility functions to help construct useful URL's
once you have a company CIK, submission accession number or specific file.

  * `company_href()` for linking to the company page
  * `submission_index_href()` and its family of related functions for linking
    to a specific submission and file.

## Installation
edgarWebR is available from CRAN, so can be simply installed via
```{r install, eval=FALSE}
install.packages("edgarWebR")
```

To install the development version,
```{r install_dev, eval=FALSE}
# Install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("mwaldstein/edgarWebR")
```

## Example
```{r example, cache=TRUE}
company_filings("AAPL", type = "10-K", count = 10)
```

## Related Packages
 * [XBRL](https://CRAN.R-project.org/package=XBRL) - Low level
   extration of data from XBRL financial files
 * [finstr](https://github.com/bergant/finstr) - Process XBRL to extract data,
   combine periods, and make basic financial calulations.
 * [finreportr](https://github.com/sewardlee337/finreportr) - All in one to
   pull finnacials and information from EDGAR

Code of Conduct
---------------
Please note that this project is released with a [Contributor Code of
Conduct](CONDUCT.md). By participating in this project you agree to abide by
its terms. Report violations to (micah@waldste.in).
